# Publishing to Scribd from R #

This vignette walks through the basics of how to publish documents from R to [Scribd](http://www.scribd.com/) using **rscribd**.

## Installation ##

You can install **rscribd** from CRAN:

```{r}
if(!require("rscribd")){
    install.packages("rscribd")
    library("rscribd")
}
```

A development version of **rscribd** is also available on [GitHub](http://www.github.com/leeper/rscribd), which can be installed using:

```
library("devtools")
install_github("leeper/rscribd")
```

## Setup ##

In order to use **rscribd**, you need to have [a Scribd API key](http://www.scribd.com/developers). This can be passed as the `api_key` argument to all **rscribd** functions. It is also a good idea, from a security perspective, to pass an `api_secret_key` argument, which will mean that API requests are additionally MD5-hashed to prevent unauthorized use of an API key. To sign requests, your API account must be configured in the [Scribd API options](http://www.scribd.com/account-settings/api) to have "Require API Signature" set to "Require signature". We can setup both of these arguments globally using `options`:

```{r}
load("apikeys.Rdata") # load API keys from `save`d local copy
options('scribd_api_key' = apikey)
options('scribd_secret_key' = secretkey)
```

If you are trying to build a public-facing app on top of **rscribd**, you may also want to leverage a user-specific session key returned by `scribd_login`. This allows user-specific operations without requiring users to register an API key. Once a session key is obtained, it can be passed to any **rscribd** function using the `session_key` argument (or have that argument set globally using `options(scribd_session_key)`). The session key is reasonably long lived. If this value is not specified, all operations are performed (by default) on the account associated with the API key.

## Creating a document ##

In this vignette, we'll create a simple [**knitr**](http://yihui.name/knitr/)-based literate programming document, which we will then upload to Scribd. We'll use the `knitr-minimal.Rnw` example file from **knitr**. We can start by `knit`ting the document to PDF:

```{r}
library("knitr")
invisible(file.copy(system.file("examples/knitr-minimal.Rnw", package = "knitr"),
                    "knitr-minimal.Rnw"))
system('R -e "knitr::knit2pdf(\'knitr-minimal.Rnw\', quiet=TRUE)"')
doc_output <- "knitr-minimal.pdf"
```

Then, to upload the document to Scribd, we only need one line of code:

```{r}
mydoc <- doc_upload(doc_output)
```

By default, this creates a public-facing Scribd document. It can also be made private using the `access = "private"` argument. Note how the `api_key` and `api_secret_key` are also included by default from the global options we specified above. We can take a look at the response object created by `doc_upload`:

```{r}
print(mydoc)
```

The `doc_id` element of the response is what we need to use in order to make any subsequent changes to a document. For example, we can use `doc_settings` to retrieve metadata information about a document:

```{r}
doc_settings(mydoc$doc_id)
```

If we want to change any of these settings, we could use `doc_change`:

```{r}
doc_change(mydoc$doc_id, title = "My first rscribd upload", description = "A knitr/rscribd example")
```

One could also upload revisions a revision of a document using `doc_upload` with the `doc` argument specified, like this:

```
doc_upload(doc_output, doc = mydoc)
```

This maintains the Scribd `document_id` and metadata but replaces the physical document. Using `doc_change` to update the `edition` metadata setting for the document additionally enables versioning of the document.

## Collections ##

If you upload multiple documents and wish to organize them, you can use Scribd collections to put like documents together. (You can also tag and categorize documents using `doc_change`, perhaps to make them easier for others to find.) A collection is simply a named container for one or more documents. 

To create a collection, use `coll_create`:

```{r}
mycoll <- coll_create("rscribd documents", "Collection of rscribd documents")
```

You can use `coll_update` to modify the title, description, or public access status for a collection after it is created. `coll_add` to add a document to a collection and `coll_docs` will list the documents stored in a collection:

```{r}
coll_add(mycoll, mydoc)
coll_docs(mycoll)
```

Removing a document from a collection works similarly to `coll_add`:

```{r, eval = FALSE}
coll_remove(mycoll, mydoc)
```

To delete a collection entirely, you can simply call: `coll_delete(mycoll)`.


## Embedding Scribd documents ##

Once uploaded to Scribd, it is possible to embed the document in an HTML page:

```{r, results="asis"}
cat(doc_embed(mydoc))
```


```{r cleanup, echo=FALSE, results="hide"}
unlink("knitr-minimal*")
unlink("./figure", recursive=TRUE)
```
