<!--
%\VignetteIndexEntry{Publishing with Scribd}
-->

# Publishing to Scribd from R #

This vignette walks through the basics of how to publish documents from R to [Scribd](http://www.scribd.com/) using **rscribd**.

## Installation ##

You can install **rscribd** from CRAN:

```{r}
if(!require("rscribd")){
    install.packages("rscribd")
    library("rscribd")
}
```

A development version of **rscribd** is also available on [GitHub](http://www.github.com/leeper/rscribd), which can be installed using:

```
library("devtools")
install_github("leeper/rscribd")
```

## Setup ##

In order to use **rscribd**, you need to have [a Scribd API key](http://www.scribd.com/developers). This can be passed as the `api_key` argument to all **rscribd** functions. It is also a good idea, from a security perspective, to pass an `api_secret_key` argument, which will mean that API requests are additionally MD5-hashed to prevent unauthorized use of an API key. To sign requests, your API account must be configured in the [Scribd API options](http://www.scribd.com/account-settings/api) to have "Require API Signature" set to "Require signature". We can setup both of these arguments globally using `options`:

```{r}
load("apikeys.Rdata") # load API keys from `save`d local copy
options('scribd_api_key' = apikey)
options('scribd_secret_key' = secretkey)
```

If you are trying to build a public-facing app on top of **rscribd**, you may also want to leverage a user-specific session key returned by `scribd_login`. This allows user-specific operations without requiring users to register an API key. Once a session key is obtained, it can be passed to any **rscribd** function using the `session_key` argument (or have that argument set globally using `options(scribd_session_key)`). The session key is reasonably long lived. If this value is not specified, all operations are performed (by default) on the account associated with the API key.

## Creating a document ##

In this vignette, we'll create a simple [**knitr**](http://yihui.name/knitr/)-based literate programming document, which we will then upload to Scribd. We'll use the `knitr-minimal.Rnw` example file from **knitr**. We can start by `knit`ting the document to PDF:

```{r}
library("knitr")
invisible(file.copy(system.file("examples/knitr-minimal.Rnw", package = "knitr"),
                    "knitr-minimal.Rnw"))
system('R -e "knitr::knit2pdf(\'knitr-minimal.Rnw\', quiet=TRUE)"')
doc_output <- "knitr-minimal.pdf"
```

Then, to upload the document to Scribd, we only need one line of code:

```{r}
mydoc <- doc_upload(doc_output)
```

By default, this creates a public-facing Scribd document. It can also be made private using the `access = "private"` argument. Note how the `api_key` and `api_secret_key` are also included by default from the global options we specified above. We can take a look at the response object created by `doc_upload`:

```{r}
print(mydoc)
```

The `doc_id` element of the response is what we need to use in order to make any subsequent changes to a document. For example, we can use `doc_settings` to retrieve metadata information about a document:

```{r}
doc_settings(mydoc$doc_id)
```

If we want to change any of these settings, we could use `doc_change`:

```{r}
doc_change(mydoc$doc_id, title = "My first rscribd upload", description = "A knitr/rscribd example")
```


## Results ##

This is what the resulting document looks like in an HTML-embedded Scribd reader:


<script type="text/javascript" src='http://www.scribd.com/javascripts/scribd_api.js'></script>

<div id='embedded_doc'><a href='http://www.scribd.com'>Scribd</a></div>

<script type='text/javascript'>

```{r, echo=FALSE, results="asis"}
# write out the javascript necessary to do a document embed
cat(paste0("var scribd_doc = scribd.Document.getDoc(",mydoc$doc_id,", '",mydoc$access_key,"');"))
```

  var onDocReady = function(e){
  // scribd_doc.api.setPage(3);
  }

  scribd_doc.addParam('jsapi_version', 2);
  scribd_doc.addEventListener('docReady', onDocReady);
  scribd_doc.write('embedded_doc');
</script>


```{r cleanup, echo=FALSE, results="hide"}
unlink("knitr-minimal*")
unlink("./figure", recursive=TRUE)
```

The source code to generate this embed dynamically (for example, in an R vignette like this one or in a Shiny app) is:

```
<script type="text/javascript" src='http://www.scribd.com/javascripts/scribd_api.js'></script>

<div id='embedded_doc'><a href='http://www.scribd.com'>Scribd</a></div>

<script type='text/javascript'>

    ```r, echo=FALSE, results="asis"
    # write out the javascript necessary to do a document embed
    cat(paste0("var scribd_doc = scribd.Document.getDoc(",mydoc$doc_id,", '",mydoc$access_key,"');"))
    ```

  var onDocReady = function(e){
  // scribd_doc.api.setPage(3);
  }

  scribd_doc.addParam('jsapi_version', 2);
  scribd_doc.addEventListener('docReady', onDocReady);
  scribd_doc.write('embedded_doc');
</script>
```
